Real-world Feasibility Analysis of ACT Algorithm for Robotic Manipulation on Home

### 2025-05-03 paper.tex
loss图片替换

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.21 of 2022/01/12
%
\documentclass[runningheads]{llncs}
%
\usepackage[T1]{fontenc}
% T1 fonts will be used to generate the final print and online PDFs,
% so please use T1 fonts in your manuscript whenever possible.
% Other font encondings may result in incorrect characters.
%
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{adjustbox}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{array} 
\usepackage{float}
\usepackage{multirow}
\usepackage{subcaption}
\usepackage{tabularx} % 在导言区添加此宏包
\usepackage{booktabs}  % 专业表格线
\usepackage{caption}   % 标题控制

\usepackage{cleveref}
\crefformat{figure}{\textbf{Figure~#2#1#3}}

@@

%
\begin{abstract}
Imitation learning allows robots to efficiently acquire complex tasks that are challenging to program manually. By learning from demonstrations, robots can adapt to new environments and task variations while enabling intuitive human-robot interaction. However, hardware constraints—such as motion limitations and sensory precision—often reduce its effectiveness. To mitigate these issues, we evaluate the Action Chunking with Transformers (ACT) algorithm, which reduces compounding errors and enhances learning efficiency. Through systematic experiments across three distinct task objectives under varying conditions, we assess ACT’s real-world applicability and its potential to accelerate robotic deployment.

@@

@@

\begin{figure}
\includegraphics[width=\textwidth]{fig3.pdf}
\caption{Left figure is leader arm,right figure is follower arm.} \label{fig2-1}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=0.95\textwidth]{fig4.pdf}
  \caption{Upper left figure is the initial state; upper right figure is the target state; bottom figure is the training environment} \label{fig2}
  \end{figure}

@@

\begin{figure}[htbp]
\includegraphics[width=0.85\textwidth]{fig12.pdf}
\caption{Wrist-mounted camera position adjustment.} \label{fig12}
\end{figure}

This task optimized the positioning of the wrist-mounted vision system. As shown in \cref{fig12}, the initial configuration (Position 1) exhibited tier recognition errors in multi-layered disc scenarios, primarily manifesting as erroneous grasps of second-layer discs with only a 40\% success rate. By relocating the camera to the robotic gripper's center position (Position 2), precise tier recognition was achieved, significantly improving the grasping success rate to 90\%.

To train a high-precision ACT (Action Chunking Transformer) model, this study implemented a systematic data collection protocol. Referencing hierarchical task decomposition methods~\cite{ref7}, for each atomic action (totaling 15 fundamental action units) in the Tower of Hanoi task, 40 training episodes were captured. Using illumination perturbation method~\cite{ref8}, with fixed lighting and background (gray tablecloth), following the robustness design principles for home environments ~\cite{ref9}. The first 20 episodes were conducted under standard lighting conditions, while the latter 20 episodes introduced lighting variations by adjusting the position and on/off state of a desk lamp to enhance the model's environmental robustness.Under our hardware configuration, the model achieved an average training time of 2 hours.

As shown in \cref{fig14}, each model achieved a final training loss below 0.05 after completing 80,000 training steps.

\begin{figure}[H]
\centering
\includegraphics[width=323pt]{15}
\caption{  Loss curve for the first action} \label{fig14}
\end{figure}

@@

\begin{table}[H]
  \centering
    \caption{Validation Success Rates of Decomposed Actions}\label{tab2}
    \begin{tabularx}{\textwidth}{>{\centering\arraybackslash}X >{\centering\arraybackslash}X >{\centering\arraybackslash}X >{\centering\arraybackslash}X} 
      \toprule
      \textbf{step} & \textbf{task name} & \textbf{current state} & \textbf{success rate} \\
      \midrule
    1 & move from A to B & A[1234]-B[]-C[] & 7/10 \\
    2 & move from A to C & A[123]-B[4]-C[] & 10/10 \\
    3 & move from B to C & A[12]-B[4]-C[3] & 9/10 \\
    4 & move from A to B & A[12]-B[]-C[34] & 7/10 \\
    5 & move from C to A & A[1]-B[2]-C[34] & 8/10 \\
    6 & move from C to B & A[14]-B[2]-C[3] & 10/10 \\
    7 & move from A to C & A[123]-B[4]-C[] & 10/10 \\
    8 & move from B to C & A[12]-B[4]-C[3] & 9/10 \\
    9 & move from A to B & A[12]-B[]-C[34] & 7/10 \\
    10 & move from C to A & A[1]-B[2]-C[34] & 8/10 \\
    11 & move from A to B & A[1234]-B[]-C[] & 7/10 \\
    12 & move from A to C & A[123]-B[4]-C[] & 10/10 \\
    13 & move from B to C & A[12]-B[4]-C[3] & 9/10 \\
    14 & move from A to B & A[12]-B[]-C[34] & 7/10 \\
    15 & move from C to A & A[1]-B[2]-C[34] & 8/10 \\
    \bottomrule
  \end{tabularx}
\end{table}

@@

\begin{figure}[H]
\centering
\includegraphics[width=\textwidth]{fig9.pdf}
\caption{ Training environment and task workflow} \label{fig9}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=323pt]{20}
\caption{Loss curve} \label{fig19}
\end{figure}

@@

\section{Conclusion}
The three experiments above demonstrate that the ACT algorithm can reduce costs while meeting practical task requirements, making it suitable for real-world applications like factory robotic arms and household service robots. Although still constrained by hardware limitations and the scale/quality of demonstration datasets - preventing true task generalization - its end-to-end learning approach significantly decreases deployment costs and implementation barriers, enabling rapid adaptation to diverse complex daily tasks.

>>>>

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.21 of 2022/01/12
%
\documentclass[runningheads]{llncs}
%
\usepackage[T1]{fontenc}
% T1 fonts will be used to generate the final print and online PDFs,
% so please use T1 fonts in your manuscript whenever possible.
% Other font encondings may result in incorrect characters.
%
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{adjustbox}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{array} 
\usepackage{float}
\usepackage{multirow}
\usepackage{subcaption}
\usepackage{tabularx} % 在导言区添加此宏包
\usepackage{booktabs}  % 专业表格线
\usepackage{array}     % 提供更好的列格式控制

\usepackage{caption}   % 标题控制
\captionsetup[figure]{labelfont=bf} % 强制加粗编号
\captionsetup[table]{labelfont=bf} 
\newcolumntype{C}{>{\centering\arraybackslash}X} % 定义居中列类型
\usepackage{cleveref}
\crefformat{figure}{\textbf{Figure~#2#1#3}}

@@

%
\begin{abstract}
Imitation learning allows robots to efficiently acquire complex tasks that are challenging to program manually. By learning from demonstrations, robots can adapt to new environments and task variations while enabling intuitive human-robot interaction. However, hardware constraints—such as motion limitations and sensory precision—often reduce its effectiveness. To mitigate these issues, we evaluate the Action Chunking with Transformers (ACT) algorithm, which reduces compounding errors and enhances learning efficiency. Through systematic experiments across two distinct task objectives under varying conditions, we assess ACT’s real-world applicability and its potential to accelerate robotic deployment.

@@

The dimensional information of key components is presented in \textbf{\cref{tab:dim_summary}} to clarify the model pipeline. The architecture follows a standard visual encoding and sequence modeling design: image features are first extracted and flattened, then fused with proprioceptive state and latent variables, and finally decoded into a sequence of predicted joint actions.

\begin{table}[htbp]
    \centering
    \caption{Dimensions of CVAE policy network modules}
    \label{tab:dim_summary}
    \begin{tabularx}{\textwidth}{@{}>{\hsize=0.5\hsize\centering\arraybackslash}X 
                                >{\hsize=1.0\hsize\centering\arraybackslash}X 
                                >{\hsize=0.8\hsize\centering\arraybackslash}X 
                                >{\hsize=1.7\hsize\centering\arraybackslash}X@{}}
        \toprule
        \textbf{Module} & \textbf{Input Dim} & \textbf{Output Dim} & \textbf{Function} \\
        \midrule
        CNN & $4 \times 480 \times 640 \times 3$ & $1200 \times 512$ & Visual feature extraction \\
        Encoder & $1202 \times 512$ & $1202 \times 512$ & Fuse image, joints and latent $z$ \\
        Decoder & $k \times 512$ & $k \times 14$ & Generate $k$-step action sequence \\
        \bottomrule
    \end{tabularx}
\end{table}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{fig3.pdf}
\caption{Left figure is leader arm,right figure is follower arm.} \label{fig2-1}
\end{figure}

@@

\begin{figure}
\centering
  \includegraphics[width=0.95\textwidth]{fig4.pdf}
  \caption{Upper left figure is the initial state; upper right figure is the target state; bottom figure is the training environment} \label{fig2}
  \end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=0.85\textwidth]{fig12.pdf}
\caption{Wrist-mounted camera position adjustment.} \label{fig12}
\end{figure}

For the 4-layer Tower of Hanoi task, a total of 15 atomic disk-moving actions were identified, each requiring a separate model. Referencing hierarchical task decomposition methods~\cite{ref7}, 40 training episodes were initially collected per action, with each model trained for 100,000 steps. Due to potential teleoperation errors and lighting variations (e.g., between daytime and evening)\cite{ref8}, some models showed suboptimal validation performance. To enhance robustness, following design principles for home environments\cite{ref9}, additional data were collected and retraining was performed for underperforming models.

As shown in \cref{fig14}, which illustrates the training loss curves for the first two models, all models achieved final training losses below 0.05, indicating stable convergence across the training process.

\begin{figure}
\centering
\includegraphics[width=323pt]{fig15.pdf}
\caption{  Loss curve for the first action} \label{fig14}
\end{figure}

@@

\begin{table}
  \centering
    \caption{\small Validation Success Rates of Decomposed Actions}\label{tab2}
  \begin{tabularx}{\textwidth}{
      >{\centering\arraybackslash}p{0.8cm}     % 第一列固定宽度（窄）
      >{\centering\arraybackslash}X           % 第二列自动调整
      >{\centering\arraybackslash}X  
      >{\centering\arraybackslash}X           % 第四列自动调整
      >{\centering\arraybackslash}X           % 第五列自动调整
      >{\centering\arraybackslash}X           % 第六列自动调整
    }
\toprule
    \textbf{step} & \textbf{action} & \textbf{state} & \textbf{training time} & \textbf{episodes} & \textbf{success rate} \\
   \midrule
     1 & A --> B      & A[1234]-B[]-C[]       & 2h 7m 51s  & 90 & 9/10 \\
     2 & A --> C      & A[123]-B[4]-C[]       & 2h 14m 43s & 40 & 9/10 \\
     3 & B --> C      & A[12]-B[4]-C[3]       & 2h 11m 19s & 50 & 10/10 \\
     4 & A --> B      & A[12]-B[]-C[34]       & 3h 46m 55s & 40 & 10/10 \\
     5 & C --> A      & A[1]-B[2]-C[34]       & 2h 7m 44s  & 80 & 10/10 \\
     6 & C --> B      & A[14]-B[2]-C[3]       & 2h 24m 28s & 40 & 9/10 \\
     7 & A --> B      & A[14]-B[23]-C[]       & 4h 13m 50s & 40 & 9/10 \\
     8 & A --> C      & A[1]-B[234]-C[]       & 3h 13m 1s  & 40 & 10/10 \\
     9 & B --> C      & A[]-B[234]-C[1]       & 1h 59m 21s & 70 & 10/10 \\
     10 & B --> A     & A[]-B[23]-C[14]       & 1h 58m 55s & 60 & 10/10 \\
     11 & C --> A     & A[3]-B[2]-C[14]       & 2h 5m 1s   & 50 & 10/10 \\
     12 & B --> C     & A[34]-B[2]-C[1]       & 3h 2m 31s  & 40 & 9/10 \\
     13 & A --> B     & A[34]-B[]-C[12]       & 2h 0m 38s  & 60 & 10/10 \\
     14 & A --> C     & A[3]-B[4]-C[12]       & 3h 28m 24s & 40 & 9/10 \\
     15 & B --> C     & A[]-B[4]-C[123]       & 2h 11m 32s & 70 & 10/10 \\
     \bottomrule
  \end{tabularx}
\end{table}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{fig9.pdf}
\caption{ Training environment and task workflow} \label{fig9}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=323pt]{fig8.pdf}
\caption{Loss curve} \label{fig19}
\end{figure}

@@

\section{Conclusion}
The two experiments above demonstrate that the ACT algorithm can reduce costs while meeting practical task requirements, making it suitable for real-world applications like factory robotic arms and household service robots. Although still constrained by hardware limitations and the scale/quality of demonstration datasets - preventing true task generalization - its end-to-end learning approach significantly decreases deployment costs and implementation barriers, enabling rapid adaptation to diverse complex daily tasks.
